\section{Broadening Participation Plans}\label{sec.broadpar}
AI\textsuperscript{3}'s efforts will be organized in multiple avenues as follows:



\myparagraph{Broadening Participation for Undergraduate Students.} As program-level leaders and members of the admissions committees (\textbf{SP Memik is the Director of the Computer Engineering Program at NU} in various graduate programs, and diversity committees at all partner institutions, we have contributed to increasing the number and percentage of women and minority substantially. 
%Under \textbf{Etienne-Cummings' leadership} at JHU, students have access to the Education, Outreach and Diversity Committee (composed of faculty, students and staff) to influence local decisions, organize events and resolve conflicts. We believe that our past success in recruiting and retaining women and under-represented minorities is due to providing an intellectually challenging but supporting environment. 

\textbf{SP Agar} will partner with a minority serving institution, Morgan State University, to teach his interdisciplinary course on Data Analysis and ML there remotely. 

%We will also organize a day-long tour of the Fermi National Laboratories for local undergraduate student members of The Society of Women Engineers, The National Society of Black Engineers, and the Society of Hispanic Professional Engineers. By experiencing the nation's leading particle physics and accelerator laboratory in person, the students will develop an interest in the needs of the physics discoveries that drive AI\textsuperscript{3}.

\myparagraph{Broadening Participation for Graduate Students.}
SPs will implement recruitment and retention initiatives through all graduate programs relevant to AI\textsuperscript{3} research. At NU, \textbf{Memik} is also a faculty leader of the Graduate Women in Computing Group and a founding member of Diversity Committees in both the ECE and CS Departments. 

In order to connect the graduate programs of the AI\textsuperscript{3} partners with URM+W students, the institute will maintain a strong presence at conferences with diversity focus. \textbf{Memik} has been organizing a booth for NU-CS and CE programs at the Grace Hopper Celebration for Women in Technology for the past three years. Following that model, booths will be staffed exclusively by the PIs representing their programs at the URM-W focused conferences such as the SACNAS National Diversity in STEM Conference, ACM Richard Tapia Celebration of Diversity of Computing, Grace
Hopper Celebration of Women in Computing, and the National Society of Black Engineers Convention. Expo participants at these events are provided access to the resume databases of the attendees. We will leverage this access to network with students to advertise our outreach events and recruit into our research programs. 

%\textbf{SPs Takac and Agar} will be actively seeking funding to develop a larger exhibit at a large museum (e.g. in NYC) to bring the excitement of this cross-disciplinary work to as broad an audience as possible.

\myparagraph{Other Public Outreach.} We will leverage venues such as the Science Cafes to interact with the general public. 

\myparagraph{Measuring Progress.} 