\section{Project Management and Collaboration Plan}\label{sec.mangtplan}
Our team is comprised of 
{\bf Seda Memik} is an expert on power and thermal-aware circuit and system design, and design automation. \textbf{Memik} has strong ties with the physics instrumentation in HEP. She contributed to the first prototype chip for the Endcap Timing Readout Chip developed for the CMS Endcap at HL-LHC~\cite{Liu:2019twepp}. She was involved in the late stage power and thermal modeling for the VIPRAM2D ASIC as part of a CMS L1 Tracking Trigger demonstration~\cite{Deptuch:2289503}. She has taken critical leadership roles, managing teams of faculty and collaborating with School-, and University-level administration. 
She was the Director of Graduate Studies for the former EECS Department (overseeing six graduate programs, MS and PhD in CS, CE, EE). 
She is currently the Director of the Computer Engineering Division under the ECE Department. 
She served on the University-wide Limited Submissions Committee between 2016-2019, overseeing NU-wide competition for limited submission to the most prestigious research awards of the nation. 
%She is also an elected member of the School of Engineering Promotion and Tenure Committee for the next two years and also a member of the Faculty Board for the NU Keyman Modern Turkish Studies.     


\textbf{Joshua Agar}
is an expert in the development of multichannel spectroscopy techniques in quantum materials.\cite{Pandya2019-ma,Ievlev2018-sw,Saremi2018-py,Agar2018-ew,Ievlev2018-uq, Ievlev2018-us,Damodaran2017-mv,Damodaran2017-ve,Agar2016-fx,Pandya2016-hy,Damodaran2016-dk,Agar2016-ys,Zhang2015-oz,Agar2015-sv,Agar2014-ds,Mangalam2013-ne,Mangalam2013-tw,Karthik2013-zm,Karthik2012-ad}
Agar has been leading a new wave of interdisciplinary researchers who deploy ML in science. 
%This work includes creating a custom featurization protocol for the detection of enhanced nanoscale electromechanical energy conversion in $PbZr_{0.2}Ti_{0.8}O_{3}$,\cite{Agar2018-ew,Agar2019-eq} and deploying deep neural networks (DNNs) to understand ferroelectric switching, conductive domain wall behavior, and electron energy loss spectroscopies (EELS).\cite{Agar_undated-wi,noauthor_undated-ib,Agar_undated-wi}
%Agar has ongoing efforts to deploy novel DNN architectures to extract information from experimental data and to accelerate the search for new functional materials.\cite{Agar_undated-yi,Agar2018-zu} 
Agar is actively involved in promoting open reproducible science. He is a contributor to open-source Python libraries for the storing and analysis of multidimensional scientific data (pycroscopy\cite{Somnath2018-yp} and pyUSID\cite{Somnath2018-yp}. Agar has set a new precedent for publication by including with manuscripts the data, analysis codes, and executable Jupyter notebooks papers that allow for text, code, and descriptions to be evaluated, understood and repurposed. 
As a Cross-Cutting Lead he will be responsible for coordinating the efforts in physics and fundamental AI. 



