\documentclass[10pt]{SelfArx}

\PassOptionsToPackage{usenames,dvipsnames}{xcolor}
\include{conf}
\usepackage{algorithm}
\usepackage{wrapfig}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=blue}

 
%\PaperTitle{Data Management Plan}
 
%**********
% Document
%**********
\begin{document}

\pagestyle{plain}

\todo[inline]{\large This is from my own proposal at Lehigh, needs to be changed}

\begin{center}
{\color{color1} \bf \large
Data Management Plan}
\end{center}

\subsection*{Intellectual Property}

The intellectual property to be produced in this project will be related to new scalable and distributed optimization algorithms for solving instances arising in large-scale learning problems.  The PIs will produce new numerical algorithms, theoretical results, and high performance software.

\subsection*{Archiving}

Research articles produced from this research will first be shared on Lehigh's Department of Industrial and Systems Engineering technical report website, as well as on the popular archiving websites arXiv and Optimization Online; see
\begin{itemize}
  \item \href{https://engineering.lehigh.edu/ise/research/ise-technical-reports}{https://engineering.lehigh.edu/ise/research/ise-technical-reports}
  \item \href{https://arxiv.org/}{https://arxiv.org/}
  \item \href{http://www.optimization-online.org/}{http://www.optimization-online.org/}
\end{itemize}

\subsection*{Articles and Conferences} 
 
Peer-reviewed articles will be submitted to top-tier journals such as {\em Mathematical Programming} and {\em SIAM Journal on Optimization}, or to top-tier conference proceedings such as that for the {\em International Conference on Machine Learning} (ICML), {\em Neural Information Processing Systems} (NeurIPS) and {\em International Conference on Artificial Intelligence and Statistics} (AISTATS).  All research articles will be co-authored by the PIs, their graduate students, postdocs, and collaborators.

\subsection*{Open-source Software, Data, and Numerical Results} 

Emphasis will be placed on the implementation of algorithms in open-source software for which data instances will be produced and with which computational experiments will be conducted.  The software produced will be stored and secured on Lehigh's computers, servers, external hard drives in the PIs' offices and labs, and on online data storage sites.  If requested, access to the software and output data will be provided through contact with the PIs.  The software and output data will be preserved for at least three years beyond the award period, as required by NSF guidelines.

The developed software libraries will be made available on the \href{http://optml.lehigh.edu/}{OptML @ Lehigh}'s github page; see \url{https://github.com/OptMLGroup}.  If algorithms developed in the course of this research yield commercially viable inventions, then access to the generated software and output data will be granted upon request once appropriate intellectual property disclosures and/or provisional patent filings are made.

Finally, the data acquired and preserved in the context of this proposal will further be governed by Lehigh University's policies on intellectual property, record retention, and data management. The details of these policies can be found at \href{http://www.lehigh.edu/~policy/}{www.lehigh.edu/\~{}policy/}.
 
\end{document}